A Tool for Visualizing Patterns of Spreadsheet Function Combinations

### 2016-04-23 doc/paper.tex
Reordering user study. Fixes #83

	\subsection{Positive Responses} The inclusion of formula examples, grounded in
	and linking back to the originating spreadsheets, proved to be an especial draw
	to the tool. After all, none of the participants professed themselves to be
	experts with Excel, their self-reported proficiencies ranging from "fairly
	familiar" (P2) to "not extremely familiar" (P4); even if they were experts, it
	would likely be unreasonable to expect an evenly distributed familiarity with
	the 100+ function trees available. Nevertheless, the list of actual formulae
	accessible through a node's double-click allowed the users a way to find
	examples of formulae with exactly the configuration they wanted. For example,
	as P1 explored the VLOOKUP function, even though they knew the official API
	more verbosely explained its signature, they said they could use the tool to
	collect more examples than the documentation offers. \par

	\begin{wrapfigure}{L}{.25\textwidth} \centering \includegraphics{SUM}
		\label{fig:sum} \caption{An abundance of parameters in SUM} \end{wrapfigure}

@@

	\subsection{Negative Responses} Some interaction with the tool underlined how a
	lack of contextual information may limit the tool. For example, the benefits
	described in the previous sections imply a hidden complication: if the tool
	educates through example but doesn't explicitly distinguish between good design
	and bad design, how can we be sure that people won't inadvertently learn bad
	design from it. Right now, we can't be sure; the tool would have to be
	supplemented with a distinguishing eye, informed on bad design already, and
	supplying the tool with this would take it beyond a design-agnostic view. [More
	on this in the conclusion.] \par

@@

	\begin{wrapfigure}{R}{.25\textwidth} \centering \includegraphics[scale=.5]{longIF} \label{fig:longif}
		\caption{The many possibilities of IF, argument 3, demonstrate the problem of
			having too many options.} \end{wrapfigure}

	Throughout the study, it became apparent that some of the concepts,
	particularly optional arguments, were easily lost in the representation. To
	illustrate this, consider the following two trees: \par

	[MOVED]

	The difference is, perhaps, too subtle: on the left, the tree contains
	instances of AND functions with any number of arguments, up to four; on the
	right, the tree contains only instances with exactly four arguments. In other
	words, an instance of "=AND(A1, B2, C3, D4)" would be found in both trees,
	while "=AND(A1, B2)" would be found in only the left. Though the users
	naturally did not explicitly report misinterpreting the icons, it became clear
	in their out-loud thoughts that they viewed each box as a fundamentally
	different set of possibilities in formula construction rather than just a
	specific parameter. Though we clarified the meanings when these
	misunderstandings became apparent, these events point to a failure in the tool
	to properly indicate every function with clarity.   \par

@@

>>>>

	\subsection{Use in Smell Tracking}
	\begin{wrapfigure}{O}{.25\textwidth} \centering \includegraphics{SUM}
		\label{fig:sum} \caption{An abundance of parameters in SUM} \end{wrapfigure}

@@

	\subsection{Use in Education}
	The inclusion of formula examples, grounded in
	and linking back to the originating spreadsheets, proved to be an especial draw
	to the tool. After all, none of the participants professed themselves to be
	experts with Excel, their self-reported proficiencies ranging from "fairly
	familiar" (P2) to "not extremely familiar" (P4); even if they were experts, it
	would likely be unreasonable to expect an evenly distributed familiarity with
	the 100+ function trees available. Nevertheless, the list of actual formulae
	accessible through a node's double-click allowed the users a way to find
	examples of formulae with exactly the configuration they wanted. For example,
	as P1 explored the VLOOKUP function, even though they knew the official API
	more verbosely explained its signature, they said they could use the tool to
	collect more examples than the documentation offers. \par

@@

	\subsection{Study Limitations}

	Throughout the study, it became apparent that some of the concepts,
	particularly optional arguments, were easily lost in the representation. To
	illustrate this, consider the following two trees.	
	The difference is, perhaps, too subtle: on the left, the tree contains
	instances of AND functions with any number of arguments, up to four; on the
	right, the tree contains only instances with exactly four arguments. In other
	words, an instance of "=AND(A1, B2, C3, D4)" would be found in both trees,
	while "=AND(A1, B2)" would be found in only the left. Though the users
	naturally did not explicitly report misinterpreting the icons, it became clear
	in their out-loud thoughts that they viewed each box as a fundamentally
	different set of possibilities in formula construction rather than just a
	specific parameter. Though we clarified the meanings when these
	misunderstandings became apparent, these events point to a failure in the tool
	to properly indicate every function with clarity.   \par

@@

	\begin{wrapfigure}{O}{.25\textwidth} 
		\centering 
		\includegraphics[width=.25\textwidth]{longIF} 
		\label{fig:longif}
		\caption{The many possibilities of IF, argument 3, demonstrate the problem of
			having too many options.} 
	\end{wrapfigure}
